<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bettingtools

<!-- badges: start -->
<!-- badges: end -->

The bettingtools package has functions related to working with sports betting lines. First, we provide functions to work with American, Decimal, and Implied odds in the tidy format.

## Installation

``` r
remotes::install_github("pwu97/bettingtools")
```

## Calculate zero-vig implied probabilities

We can calculate the zero-vig implied probabilities of a vector of lines. The default precision is set to 4 digits. Note that we can set the precision.

```{r example}
library(bettingtools)

calculateZeroVigProb(c(200, -180, -450, 800))

calculateZeroVigProb(-237)

calculateZeroVigProb(-237, precision = 7)
```

##  Calculate implied probabilities for two-outcome line set

We can calculate the implied probabilities for two lines by first calculating the zero-vig implied probabilities for both of them, and then normalizing them. Again, we can set the precision. 

```{r}
calculateImpliedProbPair(c(200, -220))

calculateImpliedProbPair(c(1000, -800))

calculateImpliedProbPair(c(1000, -800), precision = 7)
```

## Calculate theoretical hold

We can calculate the theoretical hold for a two-outcome line set. This corresponds to the profit a sportsbook would expect to make were a player to bet on either side of an event with all else being equal. Contrary to popular belief, larger nominal spreads doesn't necessarily mean more profit for bookies.

```{r}
calculateTheoreticalHold(c(-110, -110))

calculateTheoreticalHold(c(-1500, 875))

calculateTheoreticalHold(c(-1500, 875), precision = 7)
```

## Converting between American, Decimal, and Implied Odds

We can convert American odds to Decimal and Implied Odds.

```{r}
US2Implied(c(-250, 600, 137, -110))

US2Dec(c(-250, 600, 137, -110))

US2All(c(-250, 600, 137, -110))

Dec2Implied(c(3.17, 2.14, 2.01, 1.67))

Dec2US(c(3.17, 2.14, 2.01, 1.67))

Dec2All(c(3.17, 2.14, 2.01, 1.67))

Implied2Dec(c(.34, .54, .88, .12))

Implied2US(c(.34, .54, .88, .12))

Implied2All(c(.34, .54, .88, .12))
```

