<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bettingtools

<!-- badges: start -->
<!-- badges: end -->

The bettingtools package has functions related to working with sports betting lines.

## Installation

``` r
remotes::install_github("pwu97/bettingtools")
```

## Calculate zero-vig implied probabilities

We can calculate the zero-vig implied probabilities of a vector of lines. The default precision is set to 4 digits. Note that we can set the precision.

```{r example}
library(bettingtools)

calculateZeroVigProb(c(200, -180, -450, 800))

calculateZeroVigProb(-237)

calculateZeroVigProb(-237, precision = 7)
```

##  Calculate implied probabilities for two-outcome line set

We can calculate the implied probabilities for two lines by first calculating the zero-vig implied probabilities for both of them, and then normalizing them. Again, we can set the precision. 

```{r}
calculateImpliedProbPair(c(200, -220))

calculateImpliedProbPair(c(1000, -800))

calculateImpliedProbPair(c(1000, -800), precision = 7)
```

