<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bettingtools

<!-- badges: start -->
<!-- badges: end -->

The bettingtools package has functions related to working with sports betting lines. First, we provide functions to work with American, Decimal, and Implied odds in the tidy format.

## Installation

``` r
remotes::install_github("pwu97/bettingtools")
```

## Calculate single Kelly stake

We can calculate the percentage of one's bankroll one should bet to maximize the expected growth of one's bankroll on a single bet. Given an expected win probability, payout odds, and an optional Kelly multiplier factor, we can calculate one's optimal single Kelly stake. Note that default odds for the expected win probability is implied probability and the default odds for the payout is in decimal. We can change them accordingly to how we see fit by specifying additional parameters in our function.

```{r}
calculateKellyStake(0.53, 1.92)

calculateKellyStake(0.41, 2.56)

calculateKellyStake(0.70, -150, kelly_multiplier = 0.1, payout_odds = "us")

calculateKellyStake(0.26, 367, payout_odds = "us")

# Optimal move is to not place a bet
calculateKellyStake(0.26, -110, payout_odds = "us")
```


## Calculate zero-vig implied probabilities

We can calculate the zero-vig implied probabilities of a vector of lines. The default precision is set to 4 digits. Note that we can set the precision.

```{r example}
library(bettingtools)

calculateZeroVigProb(c(200, -180, -450, 800))

calculateZeroVigProb(-237)

calculateZeroVigProb(-237, precision = 7)
```

##  Calculate implied probabilities for two-outcome line set

We can calculate the implied probabilities for two lines by first calculating the zero-vig implied probabilities for both of them, and then normalizing them. Again, we can set the precision. 

```{r}
calculateImpliedProbPair(c(200, -220))

calculateImpliedProbPair(c(1000, -800))

calculateImpliedProbPair(c(1000, -800), precision = 7)
```

## Calculate theoretical hold

We can calculate the theoretical hold for a two-outcome line set. This corresponds to the profit a sportsbook would expect to make were a player to bet on either side of an event with all else being equal. Contrary to popular belief, larger nominal spreads doesn't necessarily mean more profit for bookies.

```{r}
calculateTheoreticalHold(c(-110, -110))

calculateTheoreticalHold(c(-1500, 875))

calculateTheoreticalHold(c(-1500, 875), precision = 7)
```

## Converting between American, Decimal, and Implied Odds

We can convert American odds to Decimal and Implied Odds.

```{r}
US2Implied(c(-250, 600, 137, -110))

US2Dec(c(-250, 600, 137, -110))

US2All(c(-250, 600, 137, -110))

Dec2Implied(c(3.17, 2.14, 2.01, 1.67))

Dec2US(c(3.17, 2.14, 2.01, 1.67))

Dec2All(c(3.17, 2.14, 2.01, 1.67))

Implied2Dec(c(.34, .54, .88, .12))

Implied2US(c(.34, .54, .88, .12))

Implied2All(c(.34, .54, .88, .12))
```

